\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Robert Rothschild} % Your name
\address{rarothsc@gmail.com, (720)-785-0488 \\
2137 Superior St. Bellingham WA, 98229}  % Your phone number and email

\begin{document}

%-------------------------------------------------
%	OBJECTIVE
%-------------------------------------------------

\begin{rSection}{OBJECTIVE}

{To find a job that allows me to exercise my strength and knowledge in software engineering.}

\end{rSection}
%-------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Science in Engineering} \hfill {2014 - 2018}
\\ 
Fort Lewis College, Durango CO

\end{rSection}

%-------------------------------------------------
%	EXPERIENCE SECTION
%-------------------------------------------------

\begin{rSection}{EXPERIENCE}

{\textbf{Engineer - The Heliospace Corporation} \hfill Jan 2017 - Current \\
Lead the company's software development effort including the creating of an API for processing Finite Element Analysis data. Maintained databases used for writing out various engineering documents such as bill of materials and material identification and usage list. Wrote and contributed to numerous technical documents given to customers. Has been on multiple hardware integration and test teams for projects such as the James Webb Space Telescope and NASA's Lunar Gateway }

{\textbf{Research Assistant - Colorado Space Grant Consortium} \hfill Jan 2014 - May 2018 \\
Participated in the robotics challenge to design, fabricate, and program a robot capable of traversing a Mars like environment. }


\end{rSection} 


%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS and
INTERESTS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Skills & Quick learner, People Management and Time management, Innovative and Creative thinking,\\ & Credit and Risk management, Decision Making, Ambitious, Hard working, Responsible and well\\ &disciplined, Good communication skills in English, Adjustable in any environment.
\\
Platforms &  MS Office.  \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}

{Impact of Digitalization, 2017.}{} \\
{UGC Add-on Diploma in Event management, 2015.}{}


\end{rSection} 


%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{KEY ACCOMPLISHMENTS}

{ Learned the Process in a very short time and competed with the tenured team.} \\
{ Processing Branch/Tele sales enquiries and respond appropriately.} \\
{ Pioneer in the newly implemented sprint program.} \\
{ Managed to build the bridge between different teams involved ( BOPS,UWS and RCS).} \\ 
{ Consolidating the queries of the team members and letting them know in case of any updates.} \\
{ Played a crucial role in process stream lining.}\\
{ Disseminated the newly implemented strategies and in depth knowledge about the process among the team in a short time.} \\


\end{rSection}


%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Cirrucular Activities} \itemsep -1pt {}   
\item 	Participated in 'Duet Dance Competition',  IIT KHARAGPUR.
\item	Won 1st prize in 'Vigyapana', Gayatri Vidya Parishad College.
\item	Won 1st prize in 'Vogue-Paper Couture', St.Joseph’s College for Women (Autonomous) 
\item	Attended a workshop on "Entrepreneurship Orientation Programme".
\item	Won 3rd prize in 'Product Launch' , Andhra Loyola college.
\item	Attended a National Seminar on 'Human Relations in contemporary Hindi literature', St.Joseph’s College for Women (Autonomous)
\item	Won 2nd Prize in Group Dance Competition, St.Joseph’s College for Women (Autonomous) 
\item	Actively participated as NSS Volunteer.
\item	Served as school captain
\item	Participated in Group Dance Competition, Andhra University

\end{rSection}

\begin{rSection}{PERSONAL INFORMATION}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Parents name and profession & Mr. Ashok Kumar, Indian Coast Guard. \\  & Mrs. Geeta Devi, Homemaker.\\
Date of Birth & 12 March 1997\\
Marital status & Unmarried.\\
Languages known & English and Hindi.\\
Special interests & Music, dancing, drawing and painting.\\
Residential address & Door no.71-31-283, Durganagar,\\ &Malkapuram, Visakhapatnam, 560011\\
\end{tabular}

\end{rSection}


\begin{rSection}{DECLARATION}

{I hereby declare that the information given above is true to the best of my knowledge. I will make it my earnest endeavour to discharge competently and carefully the duties you may be pleased to entrust me.}\\
 
Place : Visakhapatnam \hfill Pooja Panwar \\
Date :



\end{rSection}

\end{document}
