\documentclass{resume} % Use the custom resume.cls style
\usepackage{array}
\usepackage{graphicx}
\usepackage{enumitem,stix}
\usepackage{multirow}
\usepackage[T1]{fontenc}
\usepackage{tgheros}
\usepackage{multicol}
\usepackage{enumitem}
\setlength{\columnsep}{0.4cm}
\newlist{myList}{itemize}{1}
\setlist[myList]{label=$\smblksquare$,nosep}

\usepackage{todonotes}

\usepackage[left=0.6 in,top=0.6in,right=0.6 in,bottom=0.5in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\newcommand\Tstrut{\rule{0pt}{2.6ex}}         % = `top' strut
\begin{document}
\makeHeader{Robert Rothschild}{rarothsc@gmail.com}{720-785-0488}{Bellingham WA, 98229}{robrothschild.com}{www.linkedin.com/in/rob-rothschild}{github.com/rarothschild}

\begin{newSection}{EDUCATION}
{\bf Bachelor of Science in Engineering \hfill 2013 - 2017}\\
{Fort Lewis College, Durango, CO}
\end{newSection}
\vspace{4mm}

\begin{newSection}{RELEVANT KNOWLEDGE}
\vspace{-4mm}
\begin{multicols}{2}
        {
        {\bf Primary Languages:} Python, Javascript, Typescript, Matlab, Julia \\
         \vspace{1.5mm}
        {\bf Frondend:} HTML5, CSS, Solid, Astro, Tailwind, Bootstrap, JSON,  React, React Redux \\ \vspace{1.5mm}
        {\bf Backend:} SQL, Django, PocketDB, MySQL, GraphQL, GCP \\ \vspace{1.5mm}
        } \vfill\null \columnbreak
        {
        {\bf Concepts:} Site Deployment, Data Analytics, Control Systems, Path Planning, APIs, REST, CRUD, Agile \\ \vspace{1.5mm}
        {\bf Other Tools:} ROS, Git, Github, Netlify, NASTRAN/FEMAP, CAD, 3D Printing, VS Code, LaTeX
        }
    \end{multicols}
\end{newSection}
\vspace{-7mm}

\begin{newSection}{EXPERIENCE}

    \experience{WEB DEVELOPER} {January 2022 - Current}   \vspace{1mm}
    \begin{myList}
        \item Experienced in the design and creation of UI/UX layouts, as well as soliciting feedback to make the most ergonomic and aesthetically pleasing product possible. Used to working with many common frameworks like React and Tailwind but also new tools like Solid and Astro.
        \item Designed backends to manage databases and expose API endpoints to the front end. Has worked with SQL database tools like PocketDB, MySQL and Django.
        \item Using Julia to create toolboxes for image processing
        \item {\bf Project: HouseHold} [github.com/rarothschild/HouseHold] (Django, Vite, Solid JS, Tailwind)\\
        A portal for tenants to coordinate about finances, documentation, and communication with the landlord.
        \item {\bf Project: Maintainer} [github.com/rarothschild/Maintainer] (PocketDB, Solid Start, Tailwind)\\
        Keep track of all the maintenance you do on any asset you have. Use this history as quick way to get detailed insights while buying or selling an asset.
    \end{myList}\vspace{1.5mm}
    
    \experience{AEROSPACE ENGINEER - The Heliospace Corporation}{March 2017 - July 2022}
    \vspace{1mm}
    {\bf\hspace{0.6em} {James Webb Space Telescope} }
    \begin{myList}
        \item Wrote robust scripts that allowed fast on-orbit data processing for the JWST that was used at an agency level to determine hardware safety during deployment operations.
        \item Wrote scripts to calculate margin of safety for observatory requirements for various on-orbit scenarios. This includes working with ground test data, such as LIDAR and laser tracker, to validate computer models used in estimating shape.
        \item Wrote scripts that run Monte Carlo simulations on various release devices and process the results into margins of safety.
        \item Preformed verification and validation on observatory requirements, including running independent computer simulations on observatory performance, reviewing stress reports, and ensuring adequate protection of hardware.
        \item Provided oversight during integration and testing, working with teams to meet requirements and protect hardware during deployments and tests.
        \item Was a part of a Systems Engineering team responsible for mission assurance,  meeting new challenges that arose then planning and executing solutions.
        \item Provided oversight for the Sunshield Simulator, a ground test bed used to confirm nominal operations during deployment.
        \item Authored and contributed to various model validation and analysis reports.
        
    \end{myList}\vspace{1mm} \newpage

    {\bf\hspace{0.6em} {Heliophysics Environmental and Radiation Measurement Experiment Suite (HERMES)} }
    \begin{myList}
        \item Oversaw hardware during Thermal Vacuum testing, working with technicians to satisfy environmental requirements
        \item Processed shock test data to create shock response spectrum, protecting hardware from deployables.
        \item Authored and contributed to stress and test reports
        \item Edited and crosschecked Electrical Interface Control Drawings
    \end{myList}\vspace{1mm}

    {\bf\hspace{0.6em} {Radar for Europa Assessment and Sounding: Ocean to Near-surface (REASON)} }
    \begin{myList}
        \item Created GUIs and scripts for our engineers to compare FEA predictions to test data. This allowed for rapid processing of test data including Random Vibe, Sine Vibe, and Sine Burst, ensuring hardware safety between test levels.
        \item Wrote scripts to process Finite Element Analyses and generate a report of key areas in the hardware. This report includes stress screening and fastener loads analysis, and was directly inserted into MathCAD.
        \item All these tools were used on later projects, constantly iterating with engineers to imporve them
    \end{myList}\vspace{1mm}

    {\bf\hspace{0.6em} {Mars Sample Return (MSR)}}
    \begin{myList} 
        \item Designed hardware to transfer samples between rocket and satelite. Including restraint \& release mechanisms and rocket nose cones.
        \item Used to implementing NASA technical standards during conception and design 
    \end{myList}
    \vspace{1mm}

    {\bf\hspace{0.6em} {Other Tasks}}
    \begin{myList} 
        \item Designed software systems around NASA's core flight system (cFS) to control cubesats.
        \item Built tests beds for gathering hyperspectral imagery. Using 3D printing to rapidly iterate on hardware and writing command and data handling scripts. This imagery was used to create vegetation indicies as well as monitor other environmental factors.
    \end{myList}
    \vspace{1mm}
    
    \experience{RESEARCHER - Colorado Space Grant Consortium}{August 2016 - April 2018}
    \begin{myList}
        \item Designed, fabricated, and programmed a robot capable of autonomously traversing desert environments.
        \item Designed, fabricated, and programmed multiple payloads for high altitude weather balloon missions. These payloads collected electric field, radiation, and temperature data.
        \item Collected astronomical data using Fort Lewis' observatory
    \end{myList}
    \vspace{1mm}
    
    \experience{RESEARCHER - Fort Lewis College}{April 2015 - July 2015}
    \begin{myList}
        \item Programmed and lead demonstrations of Fort Lewis' Baxter Robot.
        \item Operated an autonomous boat to collect various scientific data.
        \item Processed this data into results used in publication (see publications). 
    \end{myList}

\end{newSection} 
\vspace{3mm}

\begin{newSection}{AWARDS AND HONORS}
\begin{myList}
    \item Best Obstacle Avoidance - Colorado Space Grant Consortium's Robotics Challenge
    \item Finalist - Hawk Tank Business Plan Competition - Fort Lewis College
    \item Sigma-Pi-Sigma Physics Honor Society Member
    \item Presenter at the 2015 American Institute of Aeronautics and Astronautics Annual Rocky Mountain Technical Symposium
    \item Technology Award - Chaparral High School - Parker, CO
    \item Eagle Scout - Troop 469 - Parker, CO
\end{myList}
\end{newSection}
\vspace{3.5mm}

\begin{newSection}{PUBLICATIONS}
    S.-H. Yoo, A. Stuntz, Y. Zhang, R. Rothschild, G. A. Hollinger, and R. N. Smith, “Experimental analysis of receding horizon planning for marine monitoring,” in Proceedings of The 10th International Conference on Field and Service Robotics, (Toronto, Canada), June 2015.
\end{newSection}
\vspace{3.5mm}

\begin{newSection}{REFERENCES}
\vspace{-2.5mm}
    \begin{center}
        \begin{tabular}{cc}
            \begin{tabular}{c}
                Colin Burt, Supervisor at Heliospace \\
                (714)-382-1006, cburt@helio.space
            \end{tabular} 
            &  
            \begin{tabular}{c}
                Jake Faust, Coworker at Heliospace \\
                (480)-899-7171, jake.faust@edwardjones.com
            \end{tabular}
        \end{tabular}
    \end{center}
\end{newSection}

\end{document}